\textbf{Computational Fuzzy Extractors}

### 2013-05-17 CompFuzzExt.tex
revising introduction

%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, 
The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.  A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.  Indeed, if the entropy loss is too high, the resulting secret key may be too short to be useful Traditionally, fuzzy extractors are defined as information-theoretic objects.  In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$.

@@

\paragraph {Our Negative Results}
We first study (in  \secref{sec:impossCompSecSketch}) whether it could be fruitful to relax the definition of the main building block of a fuzzy extractor, called \emph{secure sketch}.  A secure sketch provides information reconciliation: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$.  The traditional secrecy requirement of a secure sketch is that $w$ has high min-entropy conditioned on $s$.  This allows the fuzzy extractor of~\cite{DBLP:journals/siamcomp/DodisORS08}  to form the key $r$ by applying a randomness extractor~\cite{nisan1993randomness} to $w$, because randomness extractors get random strings from strings with conditional min-entropy. We call this the ``sketch-and-extract'' construction.

@@

Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$. This definition would also allow the use of a randomness extractor to get a pseudorandom key, although it would have to be a special extractor---one that has  a reconstruction procedure (see \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).  Unfortunately, this relaxation is also unlikely to be fruitful:  we prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$, which (for high-entropy sources of $w$ over the Hamming metric) matches the best information-theoretic security sketches.

@@

By considering this computational secrecy requirement, we construct the first \emph{lossless} computational fuzzy extractors (\consref{cons:informal construction}), where the derived key $r$ is as long as the entropy of the source $w$. It is uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work, but with two crucial differences.  First, the key $r$ is not extracted from $w$ like in the sketch-and-extract approach; rather $w$ ``encrypts'' $r$ in a way that is decryptable with the knowledge of some close $w'$. Second, the code used is a random linear code, which allows us to use the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey} to get a long $r$ out.

@@

Because we use a random linear code,  our decoding is limited to reconciling a logarithmic number of differences.  Unfortunately, we  cannot utilize the results that improve the decoding radius through the use of trapdoors (such as \cite{regev2005LWE}), because in a fuzzy extractor, there is no secret storage place for the trapdoor. If improved decoding algorithms are obtained for random linear codes, they will improve error-tolerance of our construction.

>>>>

%As defined in \cite{DBLP:journals/siamcomp/DodisORS08}, 
Fuzzy extractors use ideas from information-reconciliation~\cite{bennett1988privacy} and traditionally are defined as information-theoretic objects.  The entropy loss of a fuzzy extractor is the difference between the entropy of $w$ and the length of the derived key $r$.  In the information-theoretic setting, some entropy loss is necessary as the value $p$ contains enough information to reproduce $r$ from any close value $w'$. 
A goal of fuzzy extractor constructions is to minimize the entropy loss, increasing the security of the resulting application.  Indeed, if the entropy loss is too high, the resulting secret key may be too short to be useful.

@@

\paragraph {Our Negative Results}
We first study (in  \secref{sec:impossCompSecSketch}) whether it could be fruitful to relax the definition of the main building block of a fuzzy extractor, called \emph{secure sketch}.  A secure sketch is a one-round information reconciliation protocol: it  produces a public value $s$ that allows recovery of $w$ from any close value $w'$.  The traditional secrecy requirement of a secure sketch is that $w$ has high min-entropy conditioned on $s$.  This allows the fuzzy extractor of~\cite{DBLP:journals/siamcomp/DodisORS08}  to form the key $r$ by applying a randomness extractor~\cite{nisan1993randomness} to $w$, because randomness extractors produce random strings from strings with conditional min-entropy. We call this the \emph{sketch-and-extract} construction.

@@

Another possible relaxation is to require that the value $w$ is unpredictable conditioned on $s$. This definition would also allow the use of a randomness extractor to get a pseudorandom key, although it would have to be a special extractor---one that has  a reconstruction procedure (see \cite[Lemma 6]{DBLP:conf/eurocrypt/HsiaoLR07}).  Unfortunately, this relaxation is also unlikely to be fruitful:  we prove in \thref{thm:imp of unp entropy} that the unpredictability is at most $\log$ the size of the metric space minus $\log$ the volume of the ball of radius $t$.  For high-entropy sources of $w$ over the Hamming metric, this bound matches the best information-theoretic security sketches.

@@

By considering this computational secrecy requirement, we construct the first \emph{lossless} computational fuzzy extractors (\consref{cons:informal construction}), where the derived key $r$ is as long as the entropy of the source $w$. Our construction is for the Hamming metric and uses the code-offset construction~\cite{JW99},\cite[Section 5]{DBLP:journals/siamcomp/DodisORS08} used in prior work, but with two crucial differences.  First, the key $r$ is not extracted from $w$ like in the sketch-and-extract approach; rather $w$ ``encrypts'' $r$ in a way that is decryptable with the knowledge of some close $w'$. Second, the code used is a random linear code, which allows us to use the Learning with Errors~(LWE) assumption due to Regev~\cite{regev2005LWE, regevLWEsurvey} and derive a longer key $r$.

@@

Because we use a random linear code,  our decoding is limited to reconciling a logarithmic number of differences.  Unfortunately, we  cannot utilize the results that improve the decoding radius through the use of trapdoors (such as \cite{regev2005LWE}), because in a fuzzy extractor, there is no secret storage place for the trapdoor. If improved decoding algorithms are obtained for random linear codes, they will improve error-tolerance of our construction.  Given the hardness of decoding random linear codes~\cite{berlekamp1978}, we do not expect significant improvement in error-tolerance of our construction.
